\entry{pi\v{s}e}{piSe}{adj.}{sad. }\par
\entry{pugiñ}{pugiN}{adj.}{cold. }\par
\entry{pu\v{z}a}{puZa}{inan. n.}{Unit of length. A bit longer than an inch.}\par
\entry{pujun}{pu\t{dZ}un}{inan. n.}{entrance. }\par
\entry{pe\v{s}in}{peSin}{v.}{to avoid. }\par
\entry{pode}{pode}{an. n.}{cat. }\par
\entry{posim}{posim}{v.}{to stand. }\par
\entry{pan}{pan}{adp.}{at; on top of. }\par
\entry{bin\v{s}im}{binSim}{adj.}{patient. }\par
\entry{bi\v{s}e}{biSe}{inan. n.}{table. }\par
\entry{bi\v{s}en}{biSen}{adv.}{quickly. }\par
\entry{bi\v{z}ina}{biZina}{v.}{to laugh; to laugh at. }\par
\entry{bu}{bu}{adp.}{following. }\par
\entry{bum\v{s}on}{bumSon}{inan. n.}{morning. }\par
\entry{tikodo}{tikodo}{v.}{to leave. }\par
\entry{tim\v{z}a}{timZa}{inan. n.}{solstice. }\par
\entry{tiñzim}{tiNzim}{inan. n.}{flower. }\par
\entry{ti\v{s}u}{tiSu}{v.}{to hide; to cover. }\par
\entry{tun\v{z}u}{tunZu}{adj.}{happy. }\par
\entry{tego}{tego}{inan. n.}{Unit of length, \doz{1000} = \dec{1728} \v{s}udo. About one-third of a mile.}\par
\entry{te\v{z}uñ}{teZuN}{inan. n.}{everywhere. }\par
\entry{digo}{digo}{adj.}{big, large. }\par
\entry{dim\v{s}opa}{dimSopa}{an. n.}{plant seed. }\par
\entry{dim\v{z}iba}{dimZiba}{an. n.}{squirrel. }\par
\entry{dizu\v{z}a}{dizuZa}{v.}{to lose (an object). }\par
\entry{di\v{s}andu}{diSandu}{h. n.}{line (of people), queue. }\par
\entry{di\v{z}en}{diZen}{h. n.}{sibling. }\par
\entry{du}{du}{adp.}{near; next to. }\par
\entry{duga\v{s}a}{dugaSa}{inan. n.}{rainwater. }\par
\entry{duzo}{duzo}{adj.}{wild, barbaric. }\par
\entry{du\v{s}dudi}{duSdudi}{an. n.}{robin. }\par
\entry{du\v{s}am}{duSam}{h. n.}{person, human. }\par
\entry{du\v{c}i}{du\t{tS}i}{inan. n.}{autumn, fall (season). }\par
\entry{deku\v{z}e}{dekuZe}{v.}{to sag, to droop. }\par
\entry{dem}{dem}{adp.}{inside; at (a time), when. }\par
\entry{dem}{dem}{v.}{to sit. }\par
\entry{dempi}{dempi}{an. n.}{river current. }\par
\entry{demzu}{demzu}{adv.}{already. }\par
\entry{den\v{s}i}{denSi}{inan. n.}{floor, ground. }\par
\entry{den\v{s}añ}{denSaN}{an. n.}{summer. }\par
\entry{den\v{z}u}{denZu}{v.}{to write. }\par
\entry{desbo}{desbo}{v.}{to be born. }\par
\entry{desige}{desige}{adv.}{again. }\par
\entry{dese}{dese}{adv.}{probably, likely. }\par
\entry{dezu}{dezu}{h. n.}{jaguar. }\par
\entry{do}{do}{adp.}{toward. }\par
\entry{donse}{donse}{inan. n.}{house; animal nest. }\par
\entry{doñ\v{z}o}{doNZo}{inan. n.}{tree branch. }\par
\entry{dosen}{dosen}{inan. n.}{evening. }\par
\entry{do\v{s}bi}{doSbi}{v.}{to stop, to halt; to finish. }\par
\entry{do\.{z}e\v{s}o}{do\t{dz}eSo}{v.}{to jump; to hop. }\par
\entry{dan\v{s}u}{danSu}{an. n.}{fire. }\par
\entry{dasbu}{dasbu}{inan. n.}{point in time. }\par
\entry{kibe\v{s}u}{kibeSu}{h. n.}{neighbor. }\par
\entry{kiken}{kiken}{adj.}{neat. }\par
\entry{kisgan}{kisgan}{v.}{to pick up (a person). }\par
\entry{ki\v{s}i}{kiSi}{inan. n.}{light. }\par
\entry{ki\v{s}udin}{kiSudin}{adj.}{old. }\par
\entry{ki\v{z}e}{kiZe}{h. n.}{boy. }\par
\entry{ku}{ku}{v.}{to go. }\par
\entry{ku\v{s}e}{kuSe}{adv.}{slowly. }\par
\entry{kengo}{kengo}{an. n.}{action. }\par
\entry{ken\v{c}am}{ken\t{tS}am}{inan. n.}{fence. }\par
\entry{keñ}{keN}{adv.}{now; currently. }\par
\entry{ke\v{s}de}{keSde}{inan. n.}{there (\acrlong{med}, near listener). Can refer to specific place or anywhere near speaker depending on context. In contrast to \textlangle sbi\v{z}a\textrangle~and \textlangle \v{z}anti\textrangle .}\par
\entry{ke\v{s}gi}{keSgi}{v.}{to roll. }\par
\entry{ke\v{s}e}{keSe}{adv.}{in the past, a long time ago. }\par
\entry{ke\v{s}a}{keSa}{adj.}{good; well. }\par
\entry{kon}{kon}{v.}{to eat. }\par
\entry{kon}{kon}{adp.}{with (comitative). }\par
\entry{ko\v{z}e}{koZe}{inan. n.}{town; village. }\par
\entry{ka\v{z}i}{kaZi}{inan. n.}{nighttime. }\par
\entry{gidum}{gidum}{inan. n.}{daytime. }\par
\entry{ginsbu}{ginsbu}{v.}{to rise. }\par
\entry{gin\v{s}e}{ginSe}{adj.}{warm, hot. }\par
\entry{gise}{gise}{inan. n.}{mountain. }\par
\entry{getu}{getu}{adv.}{soon. }\par
\entry{gedike}{gedike}{inan. n.}{cover, lid. }\par
\entry{goda}{goda}{inan. n.}{door. }\par
\entry{go\v{s}bi}{goSbi}{adj.}{black. }\par
\entry{go\v{s}o}{goSo}{adv.}{be able to; can. }\par
\entry{gansu}{gansu}{inan. n.}{spring (season). }\par
\entry{ga\v{s}i}{gaSi}{v.}{to run. }\par
\entry{ga\v{z}esu}{gaZesu}{an. n.}{animal. }\par
\entry{ñizu}{Nizu}{v.}{walk (of an animal). }\par
\entry{ñeke}{Neke}{an. n.}{mist, fog. }\par
\entry{s-}{s}{aff.}{\acrlong{ind} verb. }\par
\entry{sbi\v{z}a}{sbiZa}{inan. n.}{here (\acrlong{prox}). Can refer to specific place or anywhere near speaker depending on context. In contrast to \textlangle ke\v{s}de\textrangle~and \textlangle \v{z}anti\textrangle .}\par
\entry{sbo}{sbo}{adp.}{facing; across from. }\par
\entry{sbaga}{sbaga}{h. n.}{sister. }\par
\entry{sde}{sde}{v.}{to have; to own; to hold. }\par
\entry{sdandi}{sdandi}{h. n.}{girl. }\par
\entry{sidu\v{s}u}{siduSu}{inan. n.}{ring, circle. }\par
\entry{sinzi}{sinzi}{v.}{to come. }\par
\entry{sukin}{sukin}{adj.}{bright. }\par
\entry{sedo}{sedo}{h. n.}{woman. }\par
\entry{seni}{seni}{inan. n.}{jungle; forest. }\par
\entry{seza}{seza}{v.}{to wait; to await, to wait for. }\par
\entry{so\v{z}a\v{s}be}{soZaSbe}{v.}{to cooperate. }\par
\entry{zige}{zige}{adp.}{around; surrounding. }\par
\entry{zeboyu}{zebo\t{dZ}u}{v.}{to sing. }\par
\entry{zodu\v{z}i}{zoduZi}{v.}{wear (headwear). }\par
\entry{zom}{zom}{h. n.}{father. }\par
\entry{zosdi}{zosdi}{v.}{to sail in a small boat. }\par
\entry{-\v{s}bi}{Sbi}{aff.}{verb with \acrlong{inan} \gls{subject}. }\par
\entry{\v{s}bedim}{Sbedim}{adv.}{tomorrow. }\par
\entry{\v{s}dim\v{s}a}{SdimSa}{inan. n.}{place, location. }\par
\entry{\v{s}deki}{Sdeki}{h. n.}{brother. }\par
\entry{\v{s}gomzi}{Sgomzi}{v.}{to visit. }\par
\entry{\v{s}ikunso}{Sikunso}{inan. n.}{ball. }\par
\entry{\v{s}ikapo}{Sikapo}{v.}{to vacation; to travel. }\par
\entry{\v{s}imki}{Simki}{adj.}{small, little. }\par
\entry{\v{s}in\v{z}e}{SinZe}{adj.}{(very) young; child. }\par
\entry{\v{s}udo}{Sudo}{inan. n.}{Unit of length, \doz{10} = \dec{12} pu\v{z}a. A bit longer than a foot.}\par
\entry{\v{s}ugu}{Sugu}{an. n.}{monkey. }\par
\entry{\v{s}umzan}{Sumzan}{an. n.}{dog. }\par
\entry{\v{s}un}{Sun}{adp.}{for (a duration). Does not apply to the \acrlong{pfv} aspect.}\par
\entry{\v{s}ebe}{Sebe}{v.}{to sleep. }\par
\entry{\v{s}ede}{Sede}{h. n.}{child. }\par
\entry{\v{s}emdin}{Semdin}{h. n.}{baby. }\par
\entry{\v{s}o}{So}{v.}{to look, to see. }\par
\entry{\v{s}oge}{Soge}{an. n.}{winter. }\par
\entry{\v{s}ogo}{Sogo}{an. n.}{river; stream. }\par
\entry{\v{s}onyu}{Son\t{dZ}u}{v.}{to fall, to drop. }\par
\entry{\v{s}o\v{z}idu}{SoZidu}{v.}{to play. }\par
\entry{\v{z}ika}{Zika}{adv.}{very; too. }\par
\entry{\v{z}inden}{Zinden}{v.}{to dance. }\par
\entry{\v{z}iwo}{Ziwo}{v.}{to hunt. }\par
\entry{-\v{z}u}{Zu}{aff.}{verb with \acrlong{an} \gls{subject}. }\par
\entry{-\v{z}u}{Zu}{aff.}{\acrlong{an} adjective. }\par
\entry{\v{z}umse}{Zumse}{v.}{to break; to cut. }\par
\entry{\v{z}unki}{Zunki}{inan. n.}{basket. }\par
\entry{\v{z}uñ}{ZuN}{adp.}{after. }\par
\entry{\v{z}u\v{s}o}{ZuSo}{adj.}{pretty, beautiful, handsome. }\par
\entry{\v{z}egun}{Zegun}{inan. n.}{walking stick. }\par
\entry{\v{z}ege}{Zege}{inan. n.}{sky. }\par
\entry{\v{z}e\v{s}e}{ZeSe}{v.}{to perform. }\par
\entry{\v{z}okaki}{Zokaki}{v.}{to live in the wilderness; to live away from civilization. }\par
\entry{\v{z}ojem}{Zo\t{dZ}em}{inan. n.}{sun. }\par
\entry{\v{z}am}{Zam}{adp.}{to (a location). }\par
\entry{\v{z}anti}{Zanti}{inan. n.}{there (\acrlong{dist}, far from both listener and speaker). Can refer to specific place or anywhere near speaker depending on context. In contrast to \textlangle sbi\v{z}a\textrangle~and \textlangle ke\v{s}de\textrangle .}\par
\entry{\v{z}a\v{s}don}{ZaSdon}{inan. n.}{snow. }\par
\entry{wisi}{wisi}{v.}{to know; to understand. }\par
\entry{ci}{\t{ts}i}{adp.}{away from. }\par
\entry{ci\v{z}oñ}{\t{ts}iZoN}{inan. n.}{school. }\par
\entry{\.{z}e}{\t{dz}e}{v.}{to give. }\par
\entry{\.{z}oge}{\t{dz}oge}{adp.}{under, below. }\par
\entry{\v{c}uzi}{\t{tS}uzi}{h. n.}{man. }\par
\entry{\v{c}o}{\t{tS}o}{adp.}{surrounded by, inside. }\par
\entry{\v{c}o\v{s}da\v{z}e}{\t{tS}oSdaZe}{v.}{to shout, to yell. }\par
\entry{\v{c}a-}{\t{tS}a}{aff.}{\acrlong{nom} adjective. }\par
\entry{ji}{\t{dZ}i}{adp.}{for the purpose of; in order to. }\par
\entry{jinka}{\t{dZ}inka}{adv.}{yesterday. }\par
\entry{ja-}{\t{dZ}a}{aff.}{\acrlong{nom} noun. }\par
\entry{i-}{i}{aff.}{\acrlong{pfv} verb. }\par
\entry{a-}{a}{aff.}{\acrlong{prog} verb. }
